Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-10-31 RegReport/paper.tex
Fix formatting bug
making a combined data file for more exploratory analysis

\address{$^{1}$Dept. of Psychology, University of Essex, UK\\
$^{2}$Dept. of Psychology, University of California, USA\\
$^{3}$School of Psychology and Vision Sciences, University of Leicester, UK\\
$^{4}$Dept. of Psychology, University of Kentucky, USA}
$^{5}$School of Psychology, University of Aberdeen, UK\\
%%%% Subject entries to be placed here %%%%
\subject{Psychology}

@@

>>>>

\address{$^{1}$Dept. of Psychology, University of Essex, UK\\
$^{2}$Dept. of Psychology, University of California, USA\\
$^{3}$School of Psychology and Vision Sciences, University of Leicester, UK\\
$^{4}$Dept. of Psychology, University of Kentucky, USA\\
$^{5}$School of Psychology, University of Aberdeen, UK}
%%%% Subject entries to be placed here %%%%
\subject{Psychology}

@@

\textcolor{red}{\textit{This article received in-principle acceptance (IPA) at Royal Society Open Science on 29 Jan 2020. The accepted Stage 1 version of the manuscript, not including results and discussion, may be founded at \url{https://osf.io/p2sjx}. This preregistration was performed prior to data collection and analysis.}}

### 2023-10-31 RegReport/paper_nomarkup.tex
making a combined data file for more exploratory analysis

>>>>

\textit{This article received in-principle acceptance (IPA) at Royal Society Open Science on 29 Jan 2020. The accepted Stage 1 version of the manuscript, not including results and discussion, may be founded at \url{https://osf.io/p2sjx}. This preregistration was performed prior to data collection and analysis.}
